Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-08 MDPI_submission.Rmd
Commit 2023-11-08 13:18

Due to the significant spatial and temporal variability of the trends, and the contributing factors, there is a constant need to monitor and investigate SDR in different sites in order to estimate the degree of variability,  and its relation to the local conditions.
In this study, we examine the trends of SDR, using ground-based measurements at Thessaloniki, Greece, for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, as derived from a CM-21 pyranometer.
<!-- goals -->
We reevaluated and extended the dataset used by @Bais2013, we applied a different algorithm for the identification of clear-/cloud-sky instances [@Reno2016; @Reno2012a], and we derived the SDR trends for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, under different sky conditions (all-sky, clear-sky and cloud-sky).
Finally, we investigated the dependence of the trends on solar zenith angle and season.

@@

```{r trendtable, echo=F}
x_latex <- knitr::kable(LT2,
                        format      = "latex",
                        booktabs    = TRUE,
                        escape      = TRUE,
                        format.args = list(digits = 4),
                        linesep     = "",
                        align       = "crrr",
                        centering   = FALSE,
                        table.envir = "table",
                        position    = "H",
                        caption     = paste0("Trends in SDR daily means for different sky conditions for the period ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), "."))

@@

```{r trendALL, echo=F, out.width='.70\\linewidth', fig.cap=paste0("Anomaly (\\%) of the daily all-sky SDR, relative to climatological values for ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), ". The black line shows the long term linear trend.")}
knitr::include_graphics("./images/LongtermTrends-2.png")
```

@@

```{r trendseasontable, echo=F}
## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]",
      # "Trend p-value",
      "Statistical signif. [%]"
      )]

rownames(spp) <- NULL
# panderOptions("table.alignment.default", "left")
# panderOptions("table.alignment.default", "center")
# pander(spp,
#        justify = c('center', 'right', 'right', 'center'),
#        split.table = Inf,
#        caption = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")

## use kable
x_latex <- knitr::kable(spp,
                        format      = "latex",
                        booktabs    = TRUE,
                        escape      = TRUE,
                        # format.args = list(digits = 3),
                        linesep     = "",
                        align       = "ccrr",
                        centering   = FALSE,
                        table.envir = "table",
                        # position    = "H",
                        caption  = "SDR linear trends of monthly anomalies for each season of the year.")

>>>>

Due to the significant spatial and temporal variability of the trends, and the contributing factors, there is a constant need to monitor and investigate SDR in different sites in order to estimate the degree of variability,  and its relation to the local conditions.
In this study, we examine the trends of SDR, using ground-based measurements at Thessaloniki, Greece, for the period `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`, as derived from a CM-21 pyranometer.
<!-- goals -->
We reevaluated and extended the dataset used by @Bais2013, we applied a different algorithm for the identification of clear-/cloud-sky instances [@Reno2016; @Reno2012a], and we derived the SDR trends for the period of study, under different sky conditions (all-sky, clear-sky and cloud-sky).
Finally, we investigated the dependence of the trends on solar zenith angle and season.

@@

```{r trendtable, echo=F}
LT2$`Sky conditions` <- sub(" sky", " skies", LT2$`Sky conditions`)
x_latex <- knitr::kable(LT2,
                        format      = "latex",
                        booktabs    = TRUE,
                        escape      = TRUE,
                        format.args = list(digits = 4),
                        linesep     = "",
                        align       = "crrr",
                        centering   = FALSE,
                        table.envir = "table",
                        position    = "H",
                        caption     = paste0("Trends in SDR daily means for different sky conditions for the period ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), "."))

@@

```{r trendALL, echo=F, out.width='.70\\linewidth', fig.cap=paste0("Anomalies (\\%) of the daily all-sky SDR, relative to climatological values for ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), ". The black line shows the long term linear trend.")}
knitr::include_graphics("./images/LongtermTrends-2.png")
```

@@

```{r trendseasontable, echo=F}
## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]",
      # "Trend p-value",
      "Statistical signif. [%]"
      )]
spp2 <- spp
## rename conditions
spp2$`Sky condition` <- sub(" sky", " skies", spp2$`Sky condition`)

rownames(spp2) <- NULL
# panderOptions("table.alignment.default", "left")
# panderOptions("table.alignment.default", "center")
# pander(spp,
#        justify = c('center', 'right', 'right', 'center'),
#        split.table = Inf,
#        caption = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")

## use kable
x_latex <- knitr::kable(spp2,
                        format      = "latex",
                        booktabs    = TRUE,
                        escape      = TRUE,
                        # format.args = list(digits = 3),
                        linesep     = "",
                        align       = "ccrr",
                        centering   = FALSE,
                        table.envir = "table",
                        # position    = "H",
                        caption  = "SDR linear trends of monthly anomalies for each season of the year.")

### 2023-11-08 MDPI_submission.tex
Commit 2023-11-08 13:18

Due to the significant spatial and temporal variability of the trends,
and the contributing factors, there is a constant need to monitor and
investigate SDR in different sites in order to estimate the degree of
variability, and its relation to the local conditions. In this study, we
examine the trends of SDR, using ground-based measurements at
Thessaloniki, Greece, for the period 1993 to 2023, as derived from a
CM-21 pyranometer. We reevaluated and extended the dataset used by
\citet{Bais2013}, we applied a different algorithm for the
identification of clear-/cloud-sky instances
\citep{Reno2016, Reno2012a}, and we derived the SDR trends for the
period 1993 to 2023, under different sky conditions (all-sky, clear-sky
and cloud-sky). Finally, we investigated the dependence of the trends on
solar zenith angle and season.

@@

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
Sky conditions & Trend [\%/year] & Statistical signif. [\%] & Days with data\\
\midrule
All sky & 0.376 & 100.00 & 10256\\
Clear sky & 0.349 & 100.00 & 10256\\
Cloudy sky & -0.276 & 99.97 & 5067\\
\bottomrule
\end{tabu}
\end{table}

@@

\caption{Anomaly (\%) of the daily all-sky SDR, relative to climatological values for 1993 - 2023. The black line shows the long term linear trend.}\label{fig:trendALL}
\end{figure}

@@

\multirow{-4}{*}{\centering\arraybackslash All sky} & Autumn & 0.4310 & 99.3\\
\cmidrule{1-4}
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{0.8260} & \cellcolor{gray!6}{100.0}\\

@@

\multirow{-4}{*}{\centering\arraybackslash Clear sky} & Autumn & 0.3670 & 97.2\\
\cmidrule{1-4}
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{-0.8820} & \cellcolor{gray!6}{98.9}\\

@@

\multirow{-4}{*}{\centering\arraybackslash Cloudy sky} & Autumn & -0.4000 & 89.5\\
\bottomrule
\end{tabu}
\end{table}

>>>>

Due to the significant spatial and temporal variability of the trends,
and the contributing factors, there is a constant need to monitor and
investigate SDR in different sites in order to estimate the degree of
variability, and its relation to the local conditions. In this study, we
examine the trends of SDR, using ground-based measurements at
Thessaloniki, Greece, for the period 1993 to 2023, as derived from a
CM-21 pyranometer. We reevaluated and extended the dataset used by
\citet{Bais2013}, we applied a different algorithm for the
identification of clear-/cloud-sky instances
\citep{Reno2016, Reno2012a}, and we derived the SDR trends for the
period of study, under different sky conditions (all-sky, clear-sky and
cloud-sky). Finally, we investigated the dependence of the trends on
solar zenith angle and season.

@@

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
Sky conditions & Trend [\%/year] & Statistical signif. [\%] & Days with data\\
\midrule
All skies & 0.376 & 100.00 & 10256\\
Clear skies & 0.349 & 100.00 & 10256\\
Cloudy skies & -0.276 & 99.97 & 5067\\
\bottomrule
\end{tabu}
\end{table}

@@

\caption{Anomalies (\%) of the daily all-sky SDR, relative to climatological values for 1993 - 2023. The black line shows the long term linear trend.}\label{fig:trendALL}
\end{figure}

@@

\multirow{-4}{*}{\centering\arraybackslash All skies} & Autumn & 0.4310 & 99.3\\
\cmidrule{1-4}
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{0.8260} & \cellcolor{gray!6}{100.0}\\

@@

\multirow{-4}{*}{\centering\arraybackslash Clear skies} & Autumn & 0.3670 & 97.2\\
\cmidrule{1-4}
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{-0.8820} & \cellcolor{gray!6}{98.9}\\

@@

\multirow{-4}{*}{\centering\arraybackslash Cloudy skies} & Autumn & -0.4000 & 89.5\\
\bottomrule
\end{tabu}
\end{table}

### 2023-11-08 appendix.tex
Commit 2023-11-05 21:09
Commit 2023-11-08 13:18

%% optional
\appendixtitles{yes} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{one} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
% \section{}

@@

\caption{Anomaly (\%) of the daily clear-sky SDR, relative to climatological values for1993 - 2023. The black line shows the long term linear trend for clear-sky conditions.}\label{fig:trendCLEAR}
\end{figure}

@@

\caption{Anomaly (\%) of the daily cloud-sky SDR, relative to climatological values for 1993 - 2023. The black line shows the long term linear trend for cloud-sky conditions.}\label{fig:trendCLOUD}
\end{figure}

>>>>

%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{one} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
% \section{}

@@

\caption{Anomalies (\%) of the daily clear-sky SDR, relative to climatological values for1993 - 2023. The black line shows the long term linear trend for clear-sky conditions.}\label{fig:trendCLEAR}
\end{figure}

@@

\caption{Anomalies (\%) of the daily cloud-sky SDR, relative to climatological values for 1993 - 2023. The black line shows the long term linear trend for cloud-sky conditions.}\label{fig:trendCLOUD}
\end{figure}
